%%%%Use this as a filler to get the template working
%%Introduction
\chapter{Experimental Setup}
%ATLAS is a multipurpose detector positioned around one of the 4 primry interaction points of the Large Hadron Collider (LHC) in Geneva, Switzerland. The LHC collides protons at a center of mass energy of 13 TeV, for Run 2, at a rate of approximately 600MHz. 
\section{Hadronic Colliders}
Hadronic colliders use two beams of non-fundamental particles, typically proton-proton or proton-antiproton. These accelerators benefit from the larger mass of the particles when compared to lepton colliders. This results in smaller synchrotron radiation in circular accelerators, as the radiation is inversely proportional to mass. This allows hadronic colliders to have a much larger center of mass energy than leptonic colliders for the same size circular ring. \newline
\indent While hadronic colliders typically have larger collision energies, they also have significantly "messier" collisions. In leptonic colliders, the only final state particles come from the colliding particles. In hadronic colliders, not all of the constituents of the hadrons interact in the hard collision. This leads to many additional particles in the final state. Additionally, each subparticle only carries a portion of the hadron momentum, it is impossible to know the exact initial energy of the collision. 
\section{Overlapping Collisions}
\section{The Large Hadron Collider}
%Source
The Large Hadron Collider (LHC) is a 27 kilometer ring underneath the Franco-Swiss border. The LHC accelerates beams of protons (or ions) to a center of mass energy of up to 13 TeV(5 TeV) in two antiparallel beams around the ring. The particles are then collided at 4 primary interaction points each of which has a dedicated detector: ATLAS, CMS, ALICE, and LHCb.
\subsection{Detector Coordinates}
%Source
Within the ATLAS detector, the interaction point defined the origin of the coordinate system. The z-axis, the longitudinal axis, runs along the beam line, the positive x-axis points toward the center of the LHC ring, and the positive y-axis points toward the surface. The detector is also described in r, ${\eta}$, ${\phi}$ coordinates. With the transverse plane, the plane perpendicular to the beam line, being described by r and ${\phi}$. The radial coordinate, r, describes the distance from the beam line. The azimuthal angle, ${\phi}$, is the angle from the x-axis around the beam line. The final coordinate, ${\eta}$, is referred to pseudorapidity and is defined as ${\eta = -ln(tan(\frac{\theta}{2}))}$. With ${\theta}$ being the angle from the y-axis. The variable ${\Delta{R}=\sqrt{\eta^{2} + \phi^{2}}}$ is used to describe the distance between detector objects.
\section{ATLAS}
%Source
The ATLAS detector is a general purpose detector and the largest on the LHC. It is a 44 meter long and 25 meter tall cylinder positioned along the beam pipe of the LHC. It is made up of concentric subsystems, each with a specialized task: the inner detector, which is responsible for measuring the charge and momentum of charged particles; the calorimeters, which are responsible for measuring the energy of different electromagnetic and hadronic particles; the muon spectrometer, which measures the momentum of minimum ionizing particles, like muons; and the magnet system, which is responsible for bending the charged particles in the detector, allowing their charge to be measured. The subdetectors feed into a vast Trigger and Data Acquisition (TDAQ) system that is responsible for selecting collision events with interesting characteristics.

\subsection{The Inner Detector}
%Source Inner detector TDR, I: https://cds.cern.ch/record/331063?ln=en
%Source Inner detector TDR, II: https://cds.cern.ch/record/331064?ln=en
%Source IBL TDR: https://cds.cern.ch/record/1291633?ln=en
The inner detector is the closest system to the beam pipe. It contains 4 separate pieces. In order of distance from the beam pipe: The Insertable B-Layer (IBL), the Pixel Detectors, the Semiconductor Tracker (SCT), and the Transition Radiation Tracker (TRT). These subsystems work together to give charged particle tracking within the pseudorapidity range of ${|\eta| < 2.5}$. \linebreak
\indent The IBL is the newest addition to the inner detector, being installed during the 2016 shutdown. It is place directly outside the beam pipe in order to maintain good vertexing and b tagging in increased pileup environments. In order to facilitate the insertion of the IBL, the beam pipe inner radius was decreased by 4 mm (from 29 mm to 25 mm). The IBL utilizes planar sensors, similar to the Pixel Detector, and 3D sensors, allowing electrons to interact to the bulk of the sensor as opposed to just the serface, and functions as a fourth pixel layer of the Pixel Detector.\linebreak
%Inner detector TDR Fig 3-1
\indent The Pixel Detectors are a network of high granularity, silicon pixels which measure the 2D position of passing charged particles. The silicon pixels are n-doped silicon wafers. A high voltage is applied to the wafer and when a charged particle passes through the silicon an electron hole pair is created. The electron drifts to the electrode and creates a signal that is read out by the electronics.  The Pixel detector barrel is divided into 3 cylindrical layers, the innermost layer is the B-layer, followed by Layer 1 and Layer 2. Each is covered in ${50\mu{m}}$ x ${300\mu{m}}$ silicon pixels. In order to ensure complete coverage, an end cap module is placed on each side of the barrel. The end-caps consist of 4 wheels, each with an inner and outer ring of trapezoid shaped silicon detectors. \linebreak
\indent The SCT is made of a barrel detector and two end-cap detectors. The barrel SCT has 4 cylindrical layers made up of pairs of 6.36 cm x 6.36 cm silicon crystals glued together along one side. The end-cap SCT tracker is made of rings of SCT modules with either silicon or galium arsenide. These rings are arranged into 9 wheels on each side of the barrel.\linebreak
\indent Outside of the silicon detectors lies the TRT. The TRT is a straw detector comprised of 50000, 4mm diameter straws in the barrel and 320000 radial straws in the end-caps. There are 420000 electronic channels, which give a spatial resolution of ${170\mu{m}}$ per straw. The straws are filled with various mixtures of xenon argon, carbon dioxide, tetrafluoromethane and nitrogen gas. When a charged particle passes through the TRT, they ionize the gas. The ionized gas is attracted to the oppositely charged straw and wire and produce a signal that is later amplified and read out. The xenon in the gas mixture allows for accurate particle identification from the transition radiation photon detection.  This gives a good discrimination between electrons and charged pions.
%%Important pieces for my analysis
%ID (for tracking, track-jets, vertex ID)
%The Inner Detector (ID) consists of 4 subsystems. The Insertable B-Layer (IBL), a silicon pixel detector, a semiconductor tracker (SCT) and transition radiation tracker (TRT).
%EM and Had calorimeter (jets, electrons)
%Muon Spectrometer 
%Trigger (lots of this)
\subsection{Calorimeters}
\subsection{Muon Detectors}
\subsection{Magnet System}
\subsection{Trigger System}
\subsubsection{L1 Trigger}
\subsubsection{High Level Trigger}
\section{Simulation}




